---
title: "Import DETECT Follow-up Interview Data"
---

```{r message=FALSE}
library(dplyr)
library(DBI)
library(odbc)
library(keyring)
library(purrr)
library(stringr)
library(readr)
library(lubridate)
library(hms)
library(testthat)
```

# Open the Connection to the FM database

You must first connect to the UTHealth VPN
Keyring notes: https://db.rstudio.com/best-practices/managing-credentials/
Keychain error: https://github.com/r-lib/keyring/issues/45#issuecomment-332491293

```{r}
con <- dbConnect(
  odbc(),
  driver   = "/Library/ODBC/FileMaker ODBC.bundle/Contents/MacOS/FileMaker ODBC",
  server   = "spsqlapwv003.sph.uthouston.edu",
  database = "DETECT",
  uid      = key_list("detect_fm_db_readonly")[1,2],
  pwd      = key_get("detect_fm_db_readonly")
)
```

# Pull tables into R as data frames

## ParticipantCallLog 

ParticipantCallLog has call log data from every call made. However, it doesn't have data for any of the screening questions.

## PhoneRecruitment

PhoneRecruitment has data for the screening questions, but only for the calls that made it that far. It doesn't have data for every call made.

## ParticipantScheduler 

ParticipantScheduler contains the date and time for the scheduled follow-up interview.

## Consent 

Consent contains information on whether a person gave consent or not.

## GiftCard

GiftCard contains one row for each gift card given out. It also contains all the follow-up interview questions.

## Participant

Participant contains info from MedStar's EPCR including the original DETECT screenings.

## Observational measures

Data collected on the observational measures layout in FM Pro during the F/U interviews. 

2021-02-08: Downloading this to check for incomplete

```{r}
walk(
  # List of tables to import
  c("ParticipantCallLog", "PhoneRecruitment", "ParticipantScheduler", 
    "Consent", "GiftCard", "Participant", "ObservationalMeasures"),
  
  # Import and add data frames to the global environment
  function(x) {
    df <- dbReadTable(con, x)
    # Convert camel case to snake case for df name
    nm <- str_replace_all(x, "(\\B)([A-Z])", "_\\2")
    nm <- str_to_lower(nm)
    assign(nm, df, envir = .GlobalEnv)
  }
)
```

# Close the connection to the database

```{r}
dbDisconnect(con)
rm(con)
```
