---
title: "DETECT Recruiting Dashboard"
# date: "Updated: `r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---

<!-- 
When refreshing, download the following to desktop:
  1. Participant scheduler
  2. Participant call log
  3. Phone recruitment
  4. Gift card
-->

<!-- 
Packages:
  1. rmarkdown
  2. dplyr
  3. DBI
  4. odbc
  5. Keyring
  6. purrr
  7. stringr
  8. hms
  9. lubridate
  10. forcats
  11. readr
  12. flexdashboard
  13. tidyr
  14. ggplot2
  15. plotly
  16. knitr
-->

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r data}
# Download call log data to desktop. The R script below reads it in and cleans it.
# source("data_call_log.R")
# source("data_participant_scheduler.R")
# source("data_gift_card.R")
# source("data_moca.R")
source("data_import.R")
```

<!-- Data Wrangling -->

```{r}
# Calculate summary statistics about calls made that will be used in the charts below
calls_per_day <- call_log %>%
  count(call_date) %>% 
  # Fill-in missing days with zero
  complete(call_date = seq(call_date[1], Sys.Date(), by = "1 day"), fill = list(n = 0)) %>% 
  # Add cumulative calls 
  mutate(cumulative_n = cumsum(n)) %>% 
  # Add call day variable
  mutate(
    day = weekdays(call_date),
    day = forcats::fct_relevel(day, "Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
  ) %>% 
  # Improve plot readability
  rename(
    Date = call_date,
    Day = day
  )
```

```{r}
# 2019-09-19: Sunil has a test record in the data. I emailed him about it. This part of the code can be deleted once he drops that record from the data. 
scheduled_ids <- filter(scheduled_ids, !is.na(scheduled_hour_f))

# Calculate summary statistics about interviews scheduled that will be used in the charts below
scheduled_per_day <- scheduled_ids %>% 
  count(scheduled_date) %>% 
  # Improve plot readability
  rename(
    Date = scheduled_date,
    n_scheduled = n
  )
```

```{r}
# Merge the calls data with the scheduled data
calls_per_day_w_scheduled <- calls_per_day %>%
  left_join(scheduled_per_day, by = "Date") %>% 
  mutate(
    n_scheduled = if_else(is.na(n_scheduled), 0L, n_scheduled),
    cumulative_scheduled = cumsum(n_scheduled)
  ) %>% 
  
  # For coloring the points on the recruiting calls plot below
  mutate(
    n_scheduled_f = case_when(
      n_scheduled == 0 ~ 1,
      n_scheduled == 1 ~ 2,
      n_scheduled >  1 ~ 3
    ),
    n_scheduled_f = factor(n_scheduled_f, levels = c(1, 2, 3), labels = c(
      "None", "1", "2 or More"
    ))
  ) %>% 
  
  # Renaming to make the plotly popovers look better
  rename(
    `N called` = n,
    `N Scheduled` = n_scheduled_f
  )
```

```{r}
# Data check
# At this point, both should be zero. We aren't making calls on the weekend. 
# A number > 0 indicates a data entry error.
# calls_per_day_w_scheduled %>% 
#   filter(Day %in% c("Saturday", "Sunday")) %>% 
#   summarise(
#     called = sum(`N called`),
#     scheduled = sum(n_scheduled)
#   )
```

```{r}
# Remove Saturday and Sunday from the data
# Primarily to get a more accurate calls per day calculation
calls_per_day_w_scheduled <- calls_per_day_w_scheduled %>% 
  filter(!Day %in% c("Saturday", "Sunday"))
```

```{r}
# Stack the data to long format to easily color the cumulative people and 
# follow-up interviews scheduled line chart
cum_calls_and_scheduled <- calls_per_day_w_scheduled %>%
  select(Date, cumulative_n, cumulative_scheduled) %>%
  tidyr::pivot_longer(-Date, names_to = "group", values_to = "n") %>% 
  
  # To improve readability
  mutate(
    group = if_else(group == "cumulative_n", "Calls", "Scheduled F/U Visits")
  )
```

```{r}
# Get means and total calls by day
# For the calls made by day of the week plot
means_by_day <- calls_per_day %>% 
  group_by(Day) %>% 
  filter(!Day %in% c("Saturday", "Sunday")) %>%
  summarise(
    mean = mean(n, na.rm = TRUE),
    total = sum(n, na.rm = TRUE)
  )
```


<!-- Dashboard starts here -->

Overview
=======================================================================

Updated: `r Sys.Date()`

Value boxes {data-width=250}
-----------------------------------------------------------------------

### Total follow-up interviews completed

```{r message=FALSE}
gauge(n_completed, min = 0, max = 2520)
```

### Total calls made

```{r}
total_calls <- nrow(call_log)
valueBox(total_calls, icon = "fa-phone")
```

### Average number of calls per day

```{r}
n_days_recruiting <- calls_per_day_w_scheduled %>% 
  filter()
mean_calls_per_day <- round(total_calls/nrow(calls_per_day_w_scheduled), 0)
valueBox(mean_calls_per_day, icon = "fa-phone")
```

### Total follow-up interviews scheduled

```{r}
total_scheduled <- max(calls_per_day_w_scheduled$cumulative_scheduled)
valueBox(total_scheduled, icon = "fa-calendar")
```

### Follow-up interview scheduling rate

```{r}
rate_scheduled <- round(total_calls/total_scheduled, 0)
scheduled_message <- paste("1 per", rate_scheduled, "calls")
valueBox(scheduled_message, icon = "fa-phone")
```

### Average number of calls made to each patient

```{r}
mean_calls <- call_log %>% count(medstar_id) %>% summarise(mean = mean(n)) %>% round(1)
valueBox(mean_calls, icon = "fa-phone")
```

Plots {data-width=750}
-----------------------------------------------------------------------

### Recruiting calls made and follow-up interviews scheduled by date

```{r}
calls_per_day_plot <- calls_per_day_w_scheduled %>% 
  ggplot(aes(Date, `N called`)) +
  geom_line(color = "#8a8a8a") +
  geom_point(aes(color = `N Scheduled`)) +
  scale_x_date("Date", date_label = "%b-%d", 
    # Make sure the x-axis includes the earliest date and today with other breakes
    # coming at 1 week intervals.
    breaks = seq(min(calls_per_day_w_scheduled$Date), Sys.Date(), "weeks")
  ) +
  scale_y_continuous("Number of Calls") +
  scale_color_manual(
    "F/U Scheduled", 
    values = c("#a60303", "#6AA2E7", "#03a606"),
    drop = FALSE
  ) +
  theme_bw() +
  theme(legend.title = element_text(size = 8))

plotly::ggplotly(calls_per_day_plot)
```

> The points on the plot above are colored according to the number of follow-up interviews scheduled on a given day.     
> Red = None, Blue = 1, Green = 2 or more.

### Cumulative people and follow-up interviews scheduled

```{r}
calls_per_day_cum_plot <- cum_calls_and_scheduled %>% 
  ggplot(aes(Date, n, col = group)) +
  geom_line() +
  geom_point() +
  scale_x_date("Date", date_label = "%b-%d", 
    # Make sure the x-axis includes the earliest date and today with other breakes
    # coming at 1 week intervals.
    breaks = seq(min(calls_per_day_w_scheduled$Date), Sys.Date(), "weeks")
  ) +
  scale_y_continuous("Number of Calls") +
  scale_color_manual("", values = c("Black", "#6AA2E7")) +
  theme_bw()

plotly::ggplotly(calls_per_day_cum_plot)
```

Call Timing {data-orientation=rows}
=======================================================================

Updated: `r Sys.Date()`

Row: called and scheduled by day
-----------------------------------------------------------------------

### Follow-up interviews scheduled by day of the week

```{r}
calls_per_day_w_scheduled %>% 
  group_by(Day) %>% 
  summarise(
    `Calls Made` = sum(`N called`),
    `F/U Interviews Scheduled` = sum(n_scheduled),
    `Percent Scheduled` = ((`F/U Interviews Scheduled` / `Calls Made`) * 100) %>% 
      round(1) %>% 
      format(nsmall = 1) %>% 
      paste0("%")
  ) %>% 
  knitr::kable(align = c("l", "c", "c", "c"))
```

### Calls made by day of the week

```{r}
# Plot calls by day
calls_by_day_plot <- calls_per_day %>% 
  filter(!Day %in% c("Saturday", "Sunday")) %>%
ggplot(aes(Day, n)) +
  geom_point(aes(col = Day)) +
  geom_segment(
    aes(
      x = c(0.75, 1.75, 2.75, 3.75, 4.75),
      y = mean,
      xend = c(1.25, 2.25, 3.25, 4.25, 5.25),
      yend = mean,
      col = Day
    ),
    size = 1.2,
    data = means_by_day
  ) +
  scale_x_discrete("Day") +
  scale_y_continuous("Number of Calls") +
  theme_classic() +
  theme(legend.position = "none")

plotly::ggplotly(calls_by_day_plot)
```

> The colored lines on the plot are the average number of calls by day.

Row: called and scheduled by time
-----------------------------------------------------------------------

### Follow-up interviews scheduled by time of day

```{r}
calls_by_time <- call_log %>% 
  count(call_hour_f) %>% 
  rename(
    `Time of Day` = call_hour_f,
    `Calls Made` = n
  )

scheduled_by_time <- scheduled_ids %>% 
  count(scheduled_hour_f, .drop = FALSE) %>% 
  rename(
    `Time of Day` = scheduled_hour_f,
    `F/U Interviews Scheduled` = n
  )

left_join(calls_by_time, scheduled_by_time, by = "Time of Day") %>% 
  mutate(
    `Percent Scheduled` = ((`F/U Interviews Scheduled` / `Calls Made`) * 100) %>%
      round(1) %>%
      format(nsmall = 1) %>%
      paste0("%")
  ) %>% 
  knitr::kable(align = c("l", "c", "c", "c"))
```

### Calls by time of day

```{r}
calls_by_time_plot <- call_log %>% 
  # Improve readability
  rename("Call Hour" = "call_hour_f") %>% 
ggplot() +
  geom_bar(aes(`Call Hour`, fill = ..count..)) +
  scale_x_discrete("Time of Day") +
  scale_y_continuous("Number of Calls") +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  ) +
  coord_flip()

plotly::ggplotly(calls_by_time_plot)
```

Call Responses
=======================================================================

Updated: `r Sys.Date()`

### Call log responses overall

```{r}
call_log %>% 
  count(response) %>% 
  arrange(desc(n)) %>% 
  mutate(
    `Cumulative Count` = cumsum(n),
    Percent = (n / sum(n) * 100) %>% round(0) %>% paste0("%"),
  ) %>% 
  rename("Response" = "response", "Count" = "n") %>% 
  knitr::kable(align = c("l", "c", "c", "c"))
```

MoCA {data-orientation=rows}
=======================================================================

Updated: `r Sys.Date()`

<!-- Load the moca data, may want to move this up later -->

```{r message=FALSE}
moca_deid <- readr::read_csv("data/moca_deid.csv")
```

Value boxes 
-----------------------------------------------------------------------

### Number of patients who give initial consent for screening

```{r}
eligibility_consent <- moca_deid %>% filter(phone_eligible_consent == "Yes") %>% nrow()
valueBox(eligibility_consent, icon = "fa-thumbs-up")
```

### Number of patients who pass hearing screen

```{r}
hearing_pass <- moca_deid %>% filter(phone_hearing_check == "Correct") %>% nrow()
valueBox(hearing_pass, icon = "fa-volume-up")
```

### Number of MoCA assessments started

```{r}
moca_started <- moca_deid %>% filter(!is.na(moca_memory1)) %>% nrow()
valueBox(moca_started, icon = "fa-notes-medical")
```

### Number of MoCA assessments completed

```{r}
moca_completed <- moca_deid %>% filter(!is.na(c_moca_orientation)) %>% nrow()
valueBox(moca_completed, icon = "fa-flag-checkered")
```

### Number of MoCA assessments passed

```{r}
moca_passed <- sum(moca_deid$c_score >= 17, na.rm = TRUE)
valueBox(moca_passed, icon = "fa-trophy")
```

Guages 
-----------------------------------------------------------------------

### Percent of patients who give initial consent for screening

```{r}
eligibility_asked <- moca_deid %>% filter(!is.na(phone_eligible_consent)) %>% nrow()
eligibility_consent_percent <- round(eligibility_consent / eligibility_asked * 100, 0)
gauge(eligibility_consent_percent, min = 0, max = 100, symbol = "%")
```

### Percent of patients who pass hearing screen if checked

```{r}
hearing_checked <- moca_deid %>% filter(!is.na(phone_hearing_check)) %>% nrow()
hearing_pass_percent <- round(hearing_pass / hearing_checked * 100, 0)
gauge(hearing_pass_percent, min = 0, max = 100, symbol = "%")
```

### Percent of MoCA assessments started if hearing screen passed

```{r}
moca_started <- moca_deid %>% filter(!is.na(moca_memory1)) %>% nrow()
moca_started_percent <- round(moca_started / hearing_pass * 100, 0)
gauge(moca_started_percent, min = 0, max = 100, symbol = "%")
```

### Percent of MoCA assessments completed if started

```{r}
moca_percent_completed <- round(moca_completed / moca_started * 100, 0)
gauge(moca_percent_completed, min = 0, max = 100, symbol = "%")
```

### Percent of MoCA assessments passed if completed

```{r}
moca_percent_passed <- round(moca_passed / moca_completed * 100, 0)
gauge(moca_percent_passed, min = 0, max = 100, symbol = "%")
```

Plots 
-----------------------------------------------------------------------

### Percent of MoCA assessment items completed

```{r}
moca_item_plot <- moca_deid %>% 
  # Keep only MoCA's that were startd
  filter(!is.na(moca_memory1)) %>% 
  # Keep only the MoCA questions (i.e. not calculated variables)
  select(
    moca_memory1, moca_memory2, moca_digit_forward, moca_digit_backward, 
    moca_vigilance, moca_serial7, moca_sentence_rep, moca_verb_fluency,
    moca_abstraction, moca_delay_recall, moca_orientation
  ) %>% 
  # Count the number completed for each question (i.e. not missing or refused)
  mutate_all(
    function(x) {
      out <- if_else(!is.na(x) & x != "Refused/hangup", 1, 0, NA_real_)
      out
    }
  ) %>% 
  summarise_all(sum) %>% 
  # Convert to a formated percentage
  mutate_all(
    function(x) {
      out <- round(x / moca_started * 100, 0)
      out
    }
  ) %>% 
  # Reshape wide to long
  tidyr::pivot_longer(
    everything(), 
    names_prefix = "moca_"
  ) %>% 
  # Clean up MoCA item names to improve readability
  mutate(
    name = case_when(
      name == "memory1"        ~ "Memory Trial 1",
      name == "memory2"        ~ "Memory Trial 2",
      name == "digit_forward"  ~ "Digits Forward",
      name == "digit_backward" ~ "Digits Backward",
      name == "vigilance"      ~ "Attention",
      name == "serial7"        ~ "Serial 7 Subtraction",
      name == "sentence_rep"   ~ "Repetition",
      name == "verb_fluency"   ~ "Verbal Fluency",
      name == "abstraction"    ~ "Abstraction",
      name == "delay_recall"   ~ "Delayed Recall",
      name == "orientation"    ~ "Orientation"
    ),
    name = factor(name) %>% 
      forcats::fct_relevel(
        "Memory Trial 1", "Memory Trial 2", "Digits Forward", "Digits Backward", 
        "Attention", "Serial 7 Subtraction", "Repetition", "Verbal Fluency",
        "Abstraction", "Delayed Recall", "Orientation"
      )
  ) %>% 
  # Make variable names more readable
  rename(
    "MoCA Item" = "name",
    "Percent Complete" = "value"
  ) %>% 

# Bar graph. Percent completed for each item.
ggplot(aes(`MoCA Item`, `Percent Complete`)) +
  geom_col(fill = "#6AA2E7") +
  geom_hline(yintercept = 100, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(hjust = 1, vjust = 1, angle = 45)
  )

plotly::ggplotly(moca_item_plot)
```