---
title: "Medic Reporting"
date: "Created: 2021-04-15 <br> Updated: `r Sys.Date()`"
---

Discussing medic reporting with Chad via email on 2021-04-15

```{r message=FALSE}
library(dplyr)
library(freqtables)
```

Everything we import in from Medstar will be in the Participant.csv file. This will include the initial DETECT screenings done by the responding medic (#1).

The follow-up DETECT screenings done by the medics for the research study (#2) will be captured in the Observational Measures.csv file.

```{r}
# Open the Connection to the FM database
# Keyring notes: https://db.rstudio.com/best-practices/managing-credentials/
# Keychain error: https://github.com/r-lib/keyring/issues/45#issuecomment-332491293
con <- DBI::dbConnect(
  odbc::odbc(),
  driver   = "/Library/ODBC/FileMaker ODBC.bundle/Contents/MacOS/FileMaker ODBC",
  server   = "spsqlapwv003.sph.uthouston.edu",
  database = "DETECT",
  uid      = keyring::key_list("detect_fm_db_readonly")[1,2],
  pwd      = keyring::key_get("detect_fm_db_readonly")
)

# Pull tables into R as data frames
participant <- DBI::dbReadTable(con, "Participant")

# Close the connection to the database
DBI::dbDisconnect(con)
rm(con)
```

How many any yes?

```{r}
detect <- participant %>% 
  select(MedstarID, xUnusualOdor:xApsReportedConfirmationNumber)
```

```{r}
detect <- detect %>% 
  mutate(
    across(
      .cols  = xUnusualOdor:xUnmetNeeds,
      .fns   = ~ .x == "Yes",
      .names = "{col}_yes"
    )
  ) %>% 
  rowwise() %>% 
  mutate(n_yes = sum(c_across(ends_with("_yes")), na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(any_yes = n_yes > 0)
```

```{r}
detect %>% 
  freq_table(any_yes)
```

How many report yes?

```{r}
detect %>% 
  freq_table(any_yes, xApsReported) %>% 
  select(row_var:percent_total, percent_row)
```

So, 62% of any_yes are not being reported.
