---
title: "Reporting Inclusion Data"
date: "Created: 2020-04-15 <br> Updated: `r Sys.Date()`"
---

# Overview

Need to collect and report data on sex/gender and race/ethnicity for my research performanc progress report (RPPR).

Specifically, this information is to be plugged into section G.4 of the RPPR.

Guidance on racial/ethnic categories: https://grants.nih.gov/grants/rppr/rppr_instruction_guide.pdf


# Load packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
Sys.setenv(TZ = "US/Central")
```

```{r message=FALSE}
library(dplyr)
library(flextable)
library(officer)
```


# Load data

```{r}
# Open the Connection to the FM database
# Keyring notes: https://db.rstudio.com/best-practices/managing-credentials/
# Keychain error: https://github.com/r-lib/keyring/issues/45#issuecomment-332491293
con <- DBI::dbConnect(
  odbc::odbc(),
  driver   = "/Library/ODBC/FileMaker ODBC.bundle/Contents/MacOS/FileMaker ODBC",
  server   = "spsqlapwv003.sph.uthouston.edu",
  database = "DETECT",
  uid      = keyring::key_list("detect_fm_db_readonly")[1,2],
  pwd      = keyring::key_get("detect_fm_db_readonly")
)

# Pull tables into R as data frames
participant <- DBI::dbReadTable(con, "Participant")
demo        <- DBI::dbReadTable(con, "SociodemographicInformation")

# Close the connection to the database
DBI::dbDisconnect(con)
rm(con)
```


# Data management

Merge sex from participant table into demographics table

```{r}
demo_nih <- demo %>% 
  left_join(select(participant, MedstarID, Sex), by = "MedstarID")
```

Recode sex

```{r}
demo_nih <- demo_nih %>% 
  mutate(
    sex_nih = if_else(Sex == "Unknown (Unable To Determine)", NA_character_, Sex),
    sex_nih = factor(sex_nih, levels = c("Female", "Male")),
    sex_nih = forcats::fct_explicit_na(sex_nih, "Unknown/Not Reported")
  )
```

Recode ethnicity

```{r}
demo_nih <- demo_nih %>% 
  mutate(
    ethnicity_nih = if_else(SodeHispanic == "Don't know", NA_character_, SodeHispanic),
    ethnicity_nih = factor(
      ethnicity_nih, 
      levels = c("No", "Yes"),
      labels = c("Not Hispanic or Latino", "Hispanic or Latino")
    ),
    ethnicity_nih = forcats::fct_explicit_na(ethnicity_nih, "Unknown/Not Reported")
  )
```

Use race categories required by NIH   
* American Indian or Alaska Native   
* Asian   
* Black or African American   
* Native Hawaiian or Other Pacific Islander   
* White   
* More Than One Race   

```{r}
demo_nih <- demo_nih %>%
  mutate(
    race_nih = case_when(
      is.na(SodeRace) ~ NA_character_,
      SodeRace == "Other" ~ NA_character_,
      # I'm not sure what the wierd ?? symbols are in "Don't know"
      # I imagine it's a UTF-8 thing.
      # Just using a regex to make NA for now.
      stringr::str_detect(SodeRace, "know") ~ NA_character_,
      SodeRace == "American Indian or Alaska Native" ~ 
        "American Indian or Alaska Native",
      SodeRace == "Asian" ~ "Asian",
      SodeRace == "Black or African American" ~ "Black or African American",
      SodeRace == "Native Hawaiian or Other Pacific Islander" ~ 
        "Native Hawaiian or Other Pacific Islander",
      SodeRace == "White" ~ "White",
      TRUE ~ "More than One Race"
    ),
    race_nih = factor(
      race_nih,
      levels = c(
        "American Indian or Alaska Native", "Asian", "Black or African American",
        "White", "More than One Race"
      )
    ),
    race_nih = forcats::fct_explicit_na(race_nih, "Unknown/Not Reported")
  )
```


# Summarize demographic characteristics

Sex

```{r}
demo_nih %>% 
  freqtables::freq_table(sex_nih)
```

Ethnicity

```{r}
demo_nih %>% 
  freqtables::freq_table(ethnicity_nih)
```

Race

```{r}
demo_nih %>% 
  freqtables::freq_table(race_nih)
```


# NIH Format

NIH uses this really weird table format. It is race by sex grouped by ethnicity.

```{r}
make_table_section <- function(cat) {
  demo_nih %>% 
    filter(ethnicity_nih == cat) %>% 
    freqtables::freq_table(race_nih, sex_nih) %>% 
    select(row_cat, col_cat, n) %>% 
    tidyr::pivot_wider(
      names_from = col_cat,
      values_from = n
    )
}
# For data checking
# make_table_section("Not Hispanic or Latino")
```

Run over all levels of ethnicity

```{r}
table <- purrr::map_dfc(
  .x = c("Not Hispanic or Latino", "Hispanic or Latino", "Unknown/Not Reported"),
  .f = make_table_section
)
```

Clean the table

```{r}
table <- table %>% 
  select(-row_cat1, -row_cat2)
```

Add totals to table

```{r}
table <- table %>% 
  # Add row totals
  mutate(Total = rowSums(select(., -row_cat), na.rm = TRUE)) %>% 
  # Add column totals
  bind_rows(
    summarise_all(., ~{
      if(is.numeric(.)) sum(., na.rm = TRUE)
      else "Total"
    })
  )
```

# Convert to flextable and add to Word document

```{r}
ft <- flextable(
  # Set the "Total" column to integer to get "5" instead of "5.000"
  table %>% 
    mutate(Total = as.integer(Total))
  ) %>% 
  
  # Remove 1 and 2 from current header labels
  set_header_labels(
    row_cat = "Racial Categories", Female1 = "Female", Male1 = "Male",
    `Unknown/Not Reported1` = "Unknown/Not Reported", Female2 = "Female",
    Male2 = "Male", `Unknown/Not Reported2` = "Unknown/Not Reported",
    Total = ""
  ) %>% 
  
  # Add new header labels
  add_header_row(values = c(
    "Racial Categories", "Not Hispanic or Latino", "", "", "Hispanic or Latino", 
    "", "", "Unknown/Not Reported Ethnicity", "", "", "Total"
  )) %>% 
  add_header_row(values = c("Racial Categories", "Ethnic Categories", rep("", 9))) %>% 
  
  # Column width: Trial and error
  # Make a table and play with properties
  # Change the width of the firt column
  width(j = 1, width = 1.43) %>% 
  # Change the width of the "Female" and "Male" columns
  width(j = c(2, 3, 5, 6, 8, 9, 11), width = 0.68) %>% 
  # Change the width of the "Unknown" columns
  width(j = c(4, 7, 10), width = 0.80) %>% 
  
  # Add border around all cells to match NIH Document
  # Also, makes merging easier
  theme_box() %>% 
  
  # Merge cells in header labels
  # Racial Categories
  merge_at(i = 1:3, j = 1, part = "header") %>% 
  # Ethnic Categories
  merge_at(i = 1, j = 2:11, part = "header") %>% 
  # Hispanic labels
  merge_at(i = 2, j = 2:4, part = "header") %>% 
  merge_at(i = 2, j = 5:7, part = "header") %>% 
  merge_at(i = 2, j = 8:10, part = "header") %>% 
  
  # Change font to times new roman 11
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Center column headings
  align(align = "center", part = "header") %>% 
  # Center body text
  align(j = 2:11, align = "center", part = "body")

# For checking
# ft
```

```{r}
doc <- read_docx("Word Template for Officer.docx") %>%
  body_add_par("") %>% 
  body_add_par("Cumulative (Actual)") %>% 
  body_add_par("") %>% 
  body_add_flextable(ft) %>% 
  body_add_par("") %>%
  body_add_par(paste("Updated: ", Sys.Date()))

# Output Word document
# Update the year and month in the file name dynamically
print(
  doc, 
  paste(Sys.Date() %>% format("%Y-%m"), " Inclusion Enrollment Report.docx")
)
```


# Session information

```{r echo=FALSE}
sessionInfo()
```