---
title: "Quick Look at Veteran Questions"
date: "Created: 2019-12-03 <br> Updated: `r Sys.Date()`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    css: custom-css.css
---

Save this template file. Replace it when you upgrade versions of RStudio. Copy and Paste into:

RStudio > Package Contents > Contents > Resources > resources > templates > r_markdown_notebook_osx.Rmd

# Overview

What is this file about? Months later, I should be able to glance at this section and know if the thing I'm looking for is in this file or not.


# Load packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
Sys.setenv(TZ = "US/Central")
```

```{r message=FALSE}
library(dplyr)
library(bfuncs)
```

```{r}
demo <- DBI::dbReadTable(con, "SociodemographicInformation")
sex <- DBI::dbReadTable(con, "ParticipantAnalytics")
```

```{r}
df <- demo %>% left_join(select(sex, MedstarID, Sex), by = "MedstarID")
```



[top](#top)


# Section 1

```{r}
df %>% 
  group_by(SodeMilitary) %>% 
  bfuncs::freq_table()
```


```{r}
df %>% 
  group_by(SodeMilitary, Sex) %>% 
  bfuncs::freq_table()
```

```{r}
df %>% 
  filter(SodeMilitary == "Yes") %>% 
  group_by(Sex, SodeUnwanted) %>% 
  bfuncs::freq_table()
```

```{r}
df %>% 
  filter(SodeMilitary == "Yes") %>% 
  group_by(SodeSexual) %>% 
  bfuncs::freq_table()
```


[top](#top)


# Session information

```{r echo=FALSE}
sessionInfo()
```